A meta-analysis of mental rotation ability in the first years of life

### 2022-04-08 code/analysis.Rmd
Fix meta-analytic models

# Overview of the different effect sizes
dat %>%
  select(id, group, yi_type, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
  print(n = Inf)

# Correlations between dependent samples
summary(included$r)
```

@@

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni)))
  ) %>%
  select(id, group, ni, yi, sei) -> dat_r

@@

# Add sampling variance based standard error
escalc(vi = vi, sei = sei, ni = ni, data = dat_r)

# # Two-level model
# res <- rma(
#   yi = yi,
#   sei = sei,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res)
# forest(res)

# Three-level model
res_mv <- rma.mv(
  yi = yi,
  sei = sei,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# Profile likelihodd plots
profile(res_mv, sigma2 = 1)
profile(res_mv, sigma2 = 2)

# # Meta-regression with age
# res_age <- rma.mv(
#   yi, vi,
#   mods = ~age_mean, random = ~ group | id, data = dat, slab = slab
# )
# print(res_age)
# forest(res_age)

# # Meta-regression with gender
# res_gender <- rma.mv(
#   yi, vi,
#   mods = ~female_percent, random = ~ group | id, data = dat, slab = slab
# )
# print(res_gender)
# forest(res_gender)

# # Meta-regression with age, gender, and their interaction
# res_full <- rma.mv(
#   yi, vi,
#   mods = ~age_mean * female_percent, random = ~ group | id, data = dat, slab = slab
# )
# print(res_full)
# forest(res_full)
```

>>>>

# Overview of the different effect sizes
dat %>%
  select(id, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
  print(n = Inf)

# Correlations between dependent samples
summary(dat$ri)
```

@@

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
    age_months = age_mean / 30.417
  ) %>%
  select(id, group, age_months, female_percent, ni, yi, sei) %>%
  # Compute sampling variance from standard errors
  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
  tibble() -> dat_r

@@

# # Two-level model
# res <- rma(
#   yi, vi,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res)
# forest(res)

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# # Profile likelihodd plots
# profile(res_mv, sigma2 = 1)
# profile(res_mv, sigma2 = 2)

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
```
